{\fontfamily{ptm}\selectfont The Proximal Point interpretation of Nesterov accelerated proximal gradient}

### 2024-08-31 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, updates

@@

                \subfloat[][a]{
                    \includegraphics*[width=10cm]{assets/drawing_Layer 1.png}

@@

                \label{steady_state}

@@

            Finally, similar remarks about the similar triangle form can be found in Ahn, Sra's paper \cite{ahn_understanding_2022} as well. 
            Finally, recall from 
            \hyperref[thm:ag_generic_stepsize_constraints]
            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
            that $\epsilon_{t + 1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$, setting $\epsilon_{t + 1} =0$ for all $t \in \N \cup \{0\}$. 
            If we choose to incorperate $\epsilon_{t + 1}$, it yields: 
            \begin{align*}
                x_{t + 1} &= z_{t + 1} + L\eta_t(z_{t + 1} - z_t) - \epsilon_{t + 1}\mathcal G_L(y_t). 
            \end{align*}
            Where $\epsilon_{t + 1}\mathcal G_L(y_t)$ can be viewed as a perturbations from the similar triangle form of the algorithm. 
        \end{remark}

>>>>

            See \hyperref[fig:1a]{Figure \ref*{fig:1a}}
            for an illustration. 

@@

                \subfloat[a][similar triangle]{
                    \includegraphics*[width=7cm]{assets/drawing_Layer 1.png}
                    \label{fig:1a}
                \subfloat[b][similar triangle with errors]{
                    \includegraphics*[width=6cm]{assets/drawing_Layer 1 copy.png}
                    \label{fig:1b}

@@

@@

            Finally, similar remarks about the similar triangle form can be found in Ahn, Sra's paper \cite{ahn_understanding_2022} as well. 
            Finally, recall from 
            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
            that $\epsilon_{t + 1} = \tilde \eta_{t + 1} - \eta_t - L^{-1}$, setting $\epsilon_{t + 1} =0$ for all $t \in \N \cup \{0\}$. 
            If we choose to incorperate $\epsilon_{t + 1}$, it yields: 
                x_{t + 1} &= z_{t + 1} + L\eta_t(z_{t + 1} - z_t) - \epsilon_{t + 1}\mathcal G_L(y_t) = x_t - (\eta_t + L^{-1} + \epsilon_{t + 1})\mathcal G_L(y_t). 
            Where $\epsilon_{t + 1}\mathcal G_L(y_t)$ can be viewed as a perturbations from the similar triangle form of the algorithm. 
            See 
            \hyperref[fig:1b]{Figure \ref*{fig:1b}}
            for an illustration for some $\epsilon_{t + 1} > 0$. 
